---
title: "Replication Codes for \"Who Gets Close to the Government Policies, and Who Steps Away?\""
author: "[Sohei Shigemura](https://soheishigemura.com/), [Jaehyun Song](https://www.jaysong.net), [Yuki Yanai](https://yukiyanai.github.io)"
date: "2021-01-07"
output: 
  html_document:
    highlight: "tango"
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```

This file contains replication codes for: [Sohei Shigemura](https://soheishigemura.com/), [Jaehyun Song](https://www.jaysong.net), and [Yuki Yanai](https://yukiyanai.github.io). 2020. "Who Gets Close to the Government Policies, and Who Steps Away?" *Japanese Journal of Electoral Studies* [選挙研究] 36(2): 139-150.


```{r}
if (!require(pacman)) install.packages("pacman")
pacman::p_load(tidyverse, cjoint, cregg)
```


```{r}
Raw_df <- read_csv("https://raw.githubusercontent.com/yukiyanai/jjes_persuasion/master/jjes2020_ShigemuraSongYanai.csv")
```


```{r}
q_abe <- with(Raw_df, 
              quantile(temp_Abe, prob = c(0.25, 0.75)))

Raw_df <- Raw_df %>%
  mutate(
    Temp_Abe   = case_when(temp_Abe >= q_abe[2] ~ "high",
                           temp_Abe <= q_abe[1] ~ "low",
                           TRUE                 ~ "middle"),
    across(c(Group, tax:status, Temp_Abe), factor),
    # Reorder levels
    # Baseline = what each article does NOT state
    emperor    = factor(emperor,    levels = c("deny", "approve")),
    immigrants = factor(immigrants, levels = c("accept", "refuse")),
    childcare  = factor(childcare,  levels = c("not improve", "improve"))
    )
```

---

## Distibution

Figure 2.
```{r}
Temp_Dist_Plot <- ggplot() +
  geom_polygon(aes(x = c(-100, 16, 16, -100), 
                   y = c(-100, -100, 600, 600)),
               fill = "gray90") +
  geom_polygon(aes(x = c(150, 66, 66, 150), 
                   y = c(-100, -100, 600, 600)),
               fill = "gray90") +
  geom_histogram(data = Raw_df %>% distinct(ID, temp_Abe),
                 aes(x = temp_Abe), color = "black", 
                 binwidth = 5) + 
  labs(x = "Feeling Thermometer Rating",
       y = "Count") + 
  scale_x_continuous(sec.axis = sec_axis( ~ .,
                                         breaks = c(8, 83),
                                         labels = c("Anit-Abe", 
                                                    "Pro-Abe"))) +
  coord_cartesian(xlim = c(0, 100), ylim = c(0, 550)) +
  theme_bw() +
  theme(text = element_text(size = 12))

plot(Temp_Dist_Plot)
```

---

## Group Assignmnet

```{r}
# Number of Respondents: 2940
length(unique(Raw_df$ID))

# Group Assignment
Raw_df %>% 
  distinct(ID, Group) %>%
  separate(col  = Group, into = c("Treat", "Justification"),
           sep  = "_", fill = "right") %>%
  group_by(Treat, Justification) %>%
  summarise(N       = n(), 
            .groups = "drop") %>%
  pivot_wider(names_from = Treat, values_from = N)
```

---

## Conjoint feature frequencies

```{r, fig.align = "center", fig.height = 6}
Raw_df %>%
  cj_freqs(selected ~ emperor + immigrants + childcare + tax + party +
             age_candidate + gender_candidate + status,
           level_order = "descending") %>%
  plot() +
  theme(legend.position = "none")
```

---

## AMCEs on the control

Figure 3
```{r}
Control_AMCE <- Raw_df %>%
  filter(Group == "Control") %>%
  cj(selected ~ tax + emperor + immigrants + childcare + party +
       age_candidate + gender_candidate + status, 
     id = ~ID, estimate = "amce") %>% 
  filter(feature %in% c("emperor", "immigrants", "childcare"),
         !is.na(std.error)) %>% 
  mutate(Attr = c("Female Emperor:\nApprove", 
                  "Immigrants:\nRefuse", 
                  "Childcare:\nImprove"),
         Attr = fct_inorder(Attr),
         Sig  = if_else(lower * upper > 0, "Sig", "Insig")) %>%
  ggplot() +
  geom_hline(yintercept = 0, linetype = 2) +
  geom_pointrange(aes(x = fct_rev(Attr), y = estimate, 
                      ymin = lower, ymax = upper, color = Sig),
                  show.legend = FALSE) +
  scale_color_manual(values = c("Sig" = "black", "Insig" = "gray70")) +
  labs(x = "", y = "AMCEs") +
  coord_flip() +
  theme_bw() +
  theme(text = element_text(size = 12))

plot(Control_AMCE)
```

---

## Persuasion Effects

Figure 4.
```{r}
Framing_Effect_fit <- Raw_df %>%
  cj(selected ~ tax + emperor + immigrants + childcare + party +
       age_candidate + gender_candidate + status, 
     id = ~ ID, estimate = "amce_diff",
     by = ~ Group)

Framing_Effect_plot <- Framing_Effect_fit %>%
  select(Group, feature, level, estimate, lower, upper) %>% 
  filter(feature %in% c("emperor", "immigrants", "childcare"),
         (feature == "emperor" & str_sub(Group, 1, 2) == "T1") | 
           (feature == "immigrants" & str_sub(Group, 1, 2) == "T2") | 
           (feature == "childcare" & str_sub(Group, 1, 2) == "T3")) %>%
  separate(col = Group, into = c("Treat", "Justification"), 
           sep = "_", fill = "right") %>%
  mutate(Justification = ifelse(is.na(Justification), "No", Justification),
         Justification = factor(Justification,
                                levels = c("No", "Left", "Right"),
                                labels = c("No",
                                           "Leftish",
                                           "Rightish")),
         feature       = factor(feature, 
                                levels = c("emperor", "immigrants", "childcare"),
                                labels = c("Female Emperor Approval", 
                                           "Immigrants Refusal", 
                                           "Childcare Expansion")),
         Sig           = if_else(lower * upper > 0, "Sig", "Insig")) %>%
  ggplot() +
  geom_hline(yintercept = 0) +
  geom_pointrange(aes(x = fct_rev(Justification), 
                      y = estimate, ymin = lower, ymax = upper,
                      color = Sig), show.legend = FALSE) +
  scale_color_manual(values = c("Sig" = "black", "Insig" = "gray70")) +
  scale_y_continuous(breaks = seq(-0.1, 0.1, by = 0.05)) +
  labs(x = "Justfication", y = "Differences of AMCEs") +
  facet_wrap(~feature) +
  coord_flip() +
  theme_bw() +
  theme(text = element_text(size = 12))

plot(Framing_Effect_plot)
```

---

## Conditioning on Attitudes toward Shinzo Abe

Figure 5.
```{r}
Temp_list <- list()
index <- 1

for (i in 1:3) {
  for (j in 1:3) {
    Temp <- Raw_df %>%
      filter(Group %in% list(c("Control", "T1", "T1_Right", "T1_Left"),
                             c("Control","T2", "T2_Right", "T2_Left"),
                             c("Control","T3", "T3_Right", "T3_Left"))[[i]],
             Temp_Abe == c("low", "middle", "high")[j]) %>% 
      mutate(Group    = fct_drop(Group)) %>%
      cj(selected ~ tax + emperor + immigrants + childcare + party +
           age_candidate + gender_candidate + status, 
         id = ~ ID, estimate = "amce_diff",
         by = ~ Group) %>% 
      filter(feature == c("emperor", "immigrants", "childcare")[i]) %>%
      select(Group, level, estimate, lower, upper) %>%
      mutate(Temp_Abe = c("low", "middle", "high")[j],
             Treat    = c("Emperor", "Immigrants", "Childcare")[i])
    
    Temp_list[[index]] <- Temp
    index <- index + 1
  }
}

Conditioned_AMCE <- bind_rows(Temp_list) %>%
  mutate(Temp_Abe = factor(Temp_Abe, levels = c("low", "middle", "high"),
                           labels = c("Anti-Abe", "Middle", "Pro-Abe")),
         Treat    = fct_inorder(Treat),
         Temp_Abe = fct_inorder(Temp_Abe)) %>%
  separate(col = Group, into = c("Group", "Justification"),
           fill = "right") %>%
  mutate(Justification = if_else(is.na(Justification), "No", 
                                 paste0(Justification, "ish")),
         Justification = fct_inorder(Justification),
         Sig           = case_when(lower * upper > 0 ~ "Significant",
                                   TRUE              ~ "Insignificant")) %>%
  ggplot() +
  geom_hline(yintercept = 0) +
  geom_pointrange(aes(x = fct_rev(Justification), 
                      y = estimate, ymin = lower, ymax = upper,
                      color = Sig), show.legend = FALSE) +
  scale_color_manual(values = c("Significant"   = "black", 
                                "Insignificant" = "gray70")) +
  labs(y = "Differences of AMCEs", x = "Justification") +
  coord_flip() +
  facet_grid(Treat ~ Temp_Abe) +
  theme_bw() +
  theme(text = element_text(size = 12))

plot(Conditioned_AMCE)
```
